% !TeX program = lualatex

% Use wgu-cv class
% -------------------------------------------------------------
\documentclass[
  date,
  number,
]{wgu-cv}

% Personal details
% -------------------------------------------------------------
\yourname{William\, G\, Underwood}
\youraddress{
  ORFE Department,
  Princeton University,
  Sherrerd Hall,
  Charlton Street,
  Princeton,
  NJ 08544,
  USA
}
\youremail{wgu2@princeton.edu}
\yourwebsite{wgunderwood.github.io}

% Begin document
% -------------------------------------------------------------
\begin{document}

\maketitle

% Bibliography
% -------------------------------------------------------------
%\renewcommand{\natexlab}[1]{}
%\nobibliography{WGUnderwood}

% Document settings
% -------------------------------------------------------------
\setlength{\emergencystretch}{2pt}

% Education
% -------------------------------------------------------------
\cvsection{EDUCATION}

\cvsubsection{Postdoctoral Research Associate in Statistics}
{University of Cambridge}
{July 2024 -- July 2026}

\begin{itemize}
  \item Advisor:
    Richard Samworth, Department of Pure Mathematics
    and Mathematical Statistics.
\end{itemize}

\cvsubsection{PhD in Operations Research \& Financial Engineering}
{Princeton University}
{Sep 2019 -- May 2024}

\begin{itemize}
  \item Dissertation:
    Estimation and Inference in Modern Nonparametric Statistics.
  \item Advisor:
    Matias Cattaneo, Department of Operations Research \& Financial Engineering.
\end{itemize}

\cvsubsection{MA in Operations Research \& Financial Engineering}
{Princeton University}
{Sep 2019 -- Sep 2021}

\bigskip

\cvsubsection{MMath in Mathematics \& Statistics}
{University of Oxford}
{Oct 2015 -- Jun 2019}

\begin{itemize}
  \item Dissertation:
    Motif-Based Spectral Clustering of Weighted Directed Networks.
  \item Supervisor:
    Mihai Cucuringu,
    Department of Statistics.
\end{itemize}

\vspace*{-4mm}

% Publications
% -------------------------------------------------------------
\cvsection{RESEARCH AND PUBLICATIONS}

\cvsubsection{Articles}{}{}
\begin{itemize}

  \item Uniform inference for kernel density estimators with dyadic data,
    with M.\ D.\ Cattaneo and Y.\ Feng. \\
    \emph{Journal of the American Statistical Association}, forthcoming,
    2024.
    \href{https://arxiv.org/abs/2201.05967}{%
    \texttt{arXiv{:}{\allowbreak}2201.05967}}%

  \item Motif-based spectral clustering of weighted directed networks,
    with A.\ Elliott and M.\ Cucuringu. \\
    \emph{Applied Network Science}, 5(62), 2020.
    \href{https://doi.org/10.1007/s41109-020-00293-z}{%
    \texttt{doi:10.1007/s41109-020-00293-z}}%

  \item Simple Poisson PCA: an algorithm for (sparse) feature extraction
    with simultaneous dimension \\ determination,
    with L.\ Smallman and A.\ Artemiou. \\
    \emph{Computational Statistics}, 35:559--577, 2019.
    \href{https://doi.org/10.1007/s00180-019-00903-0}{%
    \texttt{doi:10.1007/s00180-019-00903-0}}%

\end{itemize}

\cvsubsection{Preprints}{}{}
\begin{itemize}

  \item Inference with Mondrian random forests,
    with M.\ D.\ Cattaneo and J.\ M.\ Klusowski.
    \href{https://arxiv.org/abs/2310.09702}{%
    \texttt{arXiv{:}{\allowbreak}2310.09702}}%

  \item Yurinskii's coupling for martingales,
    with M.\ D.\ Cattaneo and R.\ P.\ Masini. \\
    \emph{Annals of Statistics}, reject and resubmit, 2023.
    \href{https://arxiv.org/abs/2210.00362}{%
    \texttt{arXiv{:}{\allowbreak}2210.00362}}%

\end{itemize}

\cvsubsection{Works in progress}{}{}
\begin{itemize}

  \item Higher-order extensions to the Lindeberg method,
    with M.\ D.\ Cattaneo and R.\ P.\ Masini

  \item Adaptive Mondrian random forests,
    with M.\ D.\ Cattaneo, R.\ Chandak and J.\ M.\ Klusowski
\end{itemize}

\cvsubsection{Presentations}{}{}
\begin{itemize}
  \item Two Sigma PhD Poster Session, Two Sigma Investments, July 2023
  \item Two Sigma PhD Research Symposium, Two Sigma Investments, June 2022
  \item Princeton Statistics Laboratory, Princeton University, September 2021
\end{itemize}

\pagebreak

\cvsubsection{Software}{}{}
\begin{itemize}

  \item MondrianForests: Mondrian random forests in Julia, 2023. \\
    GitHub:
    \href{https://github.com/WGUNDERWOOD/MondrianForests.jl}{%
    \texttt{WGUNDERWOOD/MondrianForests.jl}}%

  \item DyadicKDE: dyadic kernel density estimation in Julia, 2022.
    GitHub:
    \href{https://github.com/WGUNDERWOOD/DyadicKDE.jl}{%
    \texttt{WGUNDERWOOD/DyadicKDE.jl}}%

  \item motifcluster: motif-based spectral clustering
    of weighted directed networks in R, Python and Julia, 2020.
    GitHub:
    \href{https://github.com/WGUNDERWOOD/motifcluster}{%
    \texttt{WGUNDERWOOD/motifcluster}}%

\end{itemize}

% Awards & Funding
% -------------------------------------------------------------
\cvsection{AWARDS \& FUNDING}

\vspace*{-2mm}

\begin{itemize}
  \item School of Engineering and Applied Science Award for Excellence,
    Princeton University
    \hfill 2022%
  \item Francis Robbins Upton Fellowship in Engineering,
    Princeton University
    \hfill 2019%
  \item Royal Statistical Society Prize,
    Royal Statistical Society \& University of Oxford
    \hfill 2019%
  \item Gibbs Statistics Prize,
    University of Oxford
    \hfill 2019%
  \item James Fund for Mathematics Research Grant,
    St John's College, University of Oxford
    \hfill 2017%
  \item Casberd Scholarship,
    St John's College, University of Oxford
    \hfill 2016%
\end{itemize}

\vspace*{-4mm}

% Professional experience
% -------------------------------------------------------------
\cvsection{PROFESSIONAL EXPERIENCE}

\cvsubsection{Assistant in Instruction, Princeton University}
{}
{Sep 2020 -- May 2024}

\begin{itemize}

  \item
    ORF 499:
    Senior Thesis,
    Spring 2024

  \item
    ORF 498:
    Senior Independent Research Foundations,
    Fall 2023

  \item
    SML 201:
    Introduction to Data Science,
    Fall 2023

  \item
    ORF 363:
    Computing and Optimization,
    Spring 2023

  \item
    ORF 524:
    Statistical Theory and Methods,
    Fall 2022

  \item
    ORF 526:
    Probability Theory,
    Fall 2022

  \item
    ORF 524:
    Statistical Theory and Methods,
    Fall 2021

  \item
    ORF 245:
    Fundamentals of Statistics,
    Spring 2021

  \item
    ORF 363:
    Computing and Optimization,
    Fall 2020

\end{itemize}

\cvsubsection{Quantitative Research Intern, Two Sigma Investments}
{}
{Jun 2023 -- Aug 2023}
\vspace*{2mm}

\cvsubsection{Machine Learning Consultant, Mercury Digital Assets}
{}
{Oct 2018 -- Nov 2018}
\vspace*{2mm}

\cvsubsection{Educational Consultant, Polaris \& Dawn}
{}
{Feb 2018 -- Sep 2018}
\vspace*{2mm}

\cvsubsection{Premium Tutor, MyTutor}
{}
{Feb 2016 -- Oct 2018}
\vspace*{2mm}

\cvsubsection{Statistics and Machine Learning Research Intern,
Cardiff University}
{}
{Aug 2017 -- Sep 2017}
\vspace*{2mm}

\cvsubsection{Data Science Intern, Rolls-Royce}
{}
{Jun 2017 -- Aug 2017}

% Peer review
% -------------------------------------------------------------
\cvsection{PEER REVIEW}

Econometric Theory,
Journal of the American Statistical Association,
Journal of Business and Economic Statistics,
Journal of Causal Inference,
Journal of Econometrics,
Operations Research.

% References
% -------------------------------------------------------------
\cvsection{REFERENCES}

\vspace*{-2mm}

\begin{itemize}

  \item
    Matias D.\ Cattaneo,
    Professor,
    ORFE,
    Princeton University

  \item
    Jason M.\ Klusowski,
    Assistant Professor,
    ORFE,
    Princeton University

  \item
    Jianqing Fan,
    Professor,
    ORFE,
    Princeton University

  \item
    Ricardo P.\ Masini,
    Assistant Professor,
    Statistics,
    University of California, Davis

\end{itemize}

% End document
% -------------------------------------------------------------

\end{document}

% Local variables for AucTeX
% -------------------------------------------------------------
%%% Local Variables:
%%% mode: latex
%%% TeX-engine: luatex
%%% End:
